---
title: "Markdown code measuring the effects of AI on MNEs"
output:
  html_document:
    df_print: paged
  pdf_document: default
date: "2024-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Measuring technological distance

In this first part, we first measure the technology distance of different 4-digit IPC codes to the patents we defined as AI patents, and then we treat AI as a sector and measure the technological distance of NACE sectors to it.

## 1.1. Technological distance of 4-digit IPC codes to AI

We start by reading all patents that were linked to one of our MNEs or to their subsidiaries. These patents were already processed for allowing matching them directly to the MNE level (hence, patents from subsidiaries are allocated to their highest MNE level).  Then, we read original Orbis files of the MNEs, and match them to the patents, so we can know which NACE sectors are linked to each patent. These are the only files with IP information from Orbis, so they can't be shared. All of the remaining files used in the code are available online.

```{r, include=FALSE}
library(data.table) #for reading the big files using fread and for replacing countries names (by AI_pat for example)
library(readxl) #for reading the xlsx files
library(tidyverse) # Collection of all the good stuff like dplyr, ggplot2 ect.
library(magrittr) # For extra-piping operators (eg. %<>%)
library(EconGeo) # Economic Geography functions
library(psych) #for descriptives
library(Metrics) #for mae
library(did) #for treatment effect over distinct periods of time
library(openxlsx)
library(zoo) #for some reason the function na.locf is just in the zoo package for me now
library(vtable) #for functions st and sumtable in the statistics
library(ggcorrplot) #for correlation table

rm(list=ls())
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
#read all patents
all_patents <-fread("Input_code/Big_files_ignore/All_patents.csv")
#Now we add the nace codes:
CompaniesData1<-read_excel("Input_code/Big_files_ignore/DataCompanies1.xlsx", sheet = "Results", na = "n.a.")
CompaniesData2<-read_excel("Input_code/Big_files_ignore/DataCompanies2.xlsx", sheet = "Results", na = "n.a.")
CompaniesData3<-read_excel("Input_code/Big_files_ignore/DataCompanies3.xlsx", sheet = "Results", na = "n.a.")
CompaniesData4<-read_excel("Input_code/Big_files_ignore/DataCompanies4.xlsx", sheet = "Results", na = "n.a.")
CompaniesData5<-read_excel("Input_code/Big_files_ignore/DataCompanies5.xlsx", sheet = "Results", na = "n.a.")
CompaniesData6<-read_excel("Input_code/Big_files_ignore/DataCompanies6.xlsx", sheet = "Results", na = "n.a.")
CompaniesData <- rbind(CompaniesData1,CompaniesData2,CompaniesData3,CompaniesData4,CompaniesData5,CompaniesData6)

```

The patent file looks like this:
```{r}
head(all_patents)
```

The company files (there are six in total, there are ultimately merged into one) look like this:
```{r}
head(CompaniesData1)
```

Let's keep only the information we need:
```{r}
CompaniesData <- CompaniesData[,c(2,3,6)] 
names(CompaniesData) <- c("Company_name", "Company", "Nace_4d")
head(CompaniesData)
```

Next, we introduce AI as a technology by copying AI patents into a new dataset, and changing their 4-digit IPC codes to a code named **"Artificial_Intelligence"**. Then, we merge it back to the dataset and calculate a co-occurrance matrix of all codes.
```{r, include=FALSE}
rm(CompaniesData1,CompaniesData2,CompaniesData3,CompaniesData4,CompaniesData5,CompaniesData6)
all_patents <- left_join(all_patents, CompaniesData, by = "Company")
all_patents <- all_patents[is.na(all_patents$Nace_4d) == F,] #drops companies without Nace codes
rm(CompaniesData)
all_patents<-all_patents[,c(-7)]#excludes company name
#create the 3 functions we'll use later:
#1.create a function for fractional counting IPC codes on which patent
group_by_applnID <- function (data){
  data %>%
    group_by(PubNo) %>%
    mutate(field_weight = 1 / n()) %>%
    ungroup()
}
#2.create a function for counting the relative participation of each IPC code for each NACE sector
group_by_NACE_and_Subclass <- function (data){
  data %<>%
    group_by(Nace_4d, Subclass) %>%
    summarise(n_tech_reg = sum(field_weight)) %>%
    ungroup() %>%
    drop_na() 
}  
#3. create a function to build a square matrix that aggregates the co-occurrence one variable in regards to other (e.g., how many times two IPC codes appear in the same patent)
create_sparse_matrix <- function(i.input, j.input){
  require(Matrix)
  mat <- spMatrix(nrow = i.input %>% n_distinct(),
                  ncol = j.input %>% n_distinct(),
                  i = i.input %>% factor() %>% as.numeric(),
                  j = j.input %>% factor() %>% as.numeric(),
                  x = rep(1, i.input %>% length() ) )
  
  row.names(mat) <- i.input %>% factor() %>% levels()
  colnames(mat) <- j.input %>% factor() %>% levels()
  return(mat)
}

AI_Patents <- all_patents[all_patents$AIpatent == "Yes",] #Introduce AI as a specific subclass
AI_Patents_with_code <- distinct_at(AI_Patents, vars(PubNo,Company), .keep_all = T)#pick distinct codes at two variables
AI_Patents_with_code$Subclass <- "Artificial_Intelligence" #
AI_Patents <- rbind(AI_Patents, AI_Patents_with_code)
all_patents <- rbind(all_patents, AI_Patents)
rm(AI_Patents_with_code, AI_Patents)

#now let's create a square matrix where we see how often two IPC codes appear in the same patent
mat_tech <- create_sparse_matrix(i = all_patents %>% pull(PubNo),
                                 j = all_patents %>% pull(Subclass))

#let's convert this to a matrix that we can properly visualize:
mat_tech %<>% 
  crossprod() %>% 
  as.matrix() 
```

The co-occurrance matrix looks like this:
```{r}
print(as.matrix(mat_tech[1:20, 1:12]))
```

Let's now calculate the relatedness of every technology to AI:
```{r, include=FALSE}
mat_tech %<>% 
  relatedness(method = "cosine")
```
```{r}
print(as.matrix(mat_tech[1:20, 1:5]))
```

This matrix is saved with the name **"Matrix_relatedness_technologies_to_AI.csv"** to be used later.

## 1.2.Technological distance of NACE sectors to AI
#Let's now calculate the distance of NACE sectors to AI. Now, we copy AI patents into a new dataset and change the NACE codes from this new dataset to a code named **"AI"**. Then, we merge it back to the dataset (the AI patents created artificially before are already excluded) and calculate the relatedness of NACE sectors to the fake "AI sector".
```{r, include=FALSE}
rm(mat_tech)
all_patents <- all_patents[all_patents$Subclass != "Artificial_Intelligence",]
AIPatents<- all_patents[all_patents$AIpatent == "Yes",]#add AI as if it were an industry
AIPatents$Nace_4d <- "AI"
all_patents<-rbind(all_patents, AIPatents)#merge this new sector back to the longer dataset
rm(AIPatents)
#count total of patents of each sector, and total of AI patents;
all_patents %<>% group_by(Nace_4d) %>% 
  mutate(TotalPatents = length(unique(PubNo))) %>% #get the higher share of usage
  mutate(TotalAIPatents = length(na.omit(unique(PubNo[AIpatent == "Yes"])))) %>% 
  mutate(ShareAI = TotalAIPatents/TotalPatents) %>% 
  ungroup()
describe(all_patents$TotalPatents) 
all_patents <- all_patents[all_patents$TotalPatents >= 500,]
#Finally, let's apply the two functions we created before:
reg_tech <- group_by_applnID(all_patents) #this gets the relative participation of each IPC code on each patent
```

We first calculate the relative participation of each IPC code on each patent:
```{r}
head(reg_tech)
```
```{r, include=FALSE}
reg_tech <- group_by_NACE_and_Subclass(reg_tech) #this gets the sum of the relative participation of each code for each NACE
```

Then, we calculate the sum of the relative participation of each code for each NACE:
```{r}
head(reg_tech)
```
```{r, include=FALSE}
#let's convert this into a matrix where we have one line per NACE code, and all technologies linked to them in the columns
mat_reg_tech <- reg_tech %>%
  arrange(Subclass) %>% 
  pivot_wider(names_from = Subclass, values_from = n_tech_reg, values_fill = list(n_tech_reg = 0)) #
```  

And convert this into a matrix where we have one line per NACE code, and all technologies linked to them in the columns:  
```{r}
head(mat_reg_tech)
```

```{r, include=FALSE}
#let's throw the nace codes into the column names
mat_reg_tech %<>% remove_rownames %>% column_to_rownames(var="Nace_4d") %>%
  as.matrix() %>%
  round() 
#and calculate binary specializations
rel_sectors_codes <- mat_reg_tech %>% location_quotient(binary = T) %>% 
  as.data.frame() %>% 
  rownames_to_column("mat_reg_tech") %>% 
  as_tibble() %>% 
  gather(key = "Subclass", value = "RCA", -mat_reg_tech) %>%
  arrange(mat_reg_tech, Subclass)
```

Finally, we calculate the specializations of all sectors on each technology:
```{r}
head(rel_sectors_codes)
```
```{r, include=FALSE}
#let's transform this back into a matrix:
rel_sectors_codes %<>%
  arrange(Subclass, mat_reg_tech) %>%
  pivot_wider(names_from = Subclass, values_from = RCA, values_fill = list(RCA = 0)) #transform on a binary-like matrix
```

Let's transform this back into a matrix:
```{r}
head(rel_sectors_codes)
```

Now, we set the AI sector with its specializations as a target, and calculate the distance of all sectors to it based on MAE. The result looks like this:
```{r, include=FALSE}
#replace NA values by 0
rel_sectors_codes[is.na(rel_sectors_codes)] <- 0
#let's set the AI sector as a target/reference for calculating the distance:
predicted <- rel_sectors_codes[rel_sectors_codes$mat_reg_tech=="AI",]
predicted<- predicted[,(-1)]
predicted<-as.vector(predicted,mode='numeric')
#let's calculate the distance from all sectors to this AI reference:
AverageDistance <- as.data.frame("Nace_4d", col.names = "a")

for (i in 1:length(rel_sectors_codes$mat_reg_tech)){
  
  AverageDistance[i] <- mae(as.vector(rel_sectors_codes[i,][,(-1)],mode='numeric'),predicted)
}
AverageDistance <- as.data.frame(t(AverageDistance))
Sectors <- as.data.frame(rel_sectors_codes[,1])
AverageDistance <- cbind(AverageDistance,Sectors)
names(AverageDistance) <- c("AverageDistance", "Nace_4d")
#let's create the group category based on quartiles. the lower the distance to AI, the closer the sector is to it
AverageDistance$Quartile <- ifelse(AverageDistance$AverageDistance>=quantile(AverageDistance$AverageDistance)[[4]], "bottom",
                                                ifelse(AverageDistance$AverageDistance<quantile(AverageDistance$AverageDistance)[[4]] & 
                                                         AverageDistance$AverageDistance>quantile(AverageDistance$AverageDistance)[[2]], "medium", "top"))
```
```{r}
head(AverageDistance)
```

This file is saved with the name **"Distance_NACE_sectors_to_AI.csv"**

# 2.Measuring effects
## 2.1.Overall
### 2.1.1.Non-standard - Relatedness and number of patents regardless of sector
```{r, include=FALSE}
rm(list=ls())
DataLong_Subs_sim <- read.csv("Input_code/Matched_companies.csv", sep = ";", header = TRUE, dec=",") #

#1.1.1.Simple Aggregation Relatedness
example_attgt <- att_gt(yname = "Relatedness_Cos2", tname = "CurrentYear", idname = "id",
                        gname = "first.treat", xformla = ~1, data = DataLong_Subs_sim, alp=.01
)

agg.simple <- aggte(example_attgt, type = "simple", na.rm = TRUE)
```

First we calculate the overall effects on relatedness. The results are:
```{r}
summary(agg.simple) 
```

```{r, include=FALSE}
agg.es <- aggte(example_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es)
Fig<- ggdid(agg.es, title = "H1) All quartiles - Relatedness") + theme(legend.position="right") +   ylab("Knowledge-relatedness") + 
  xlab("Length of exposure") + scale_color_manual(values=c("grey70","orange"),labels = c("Pre-treatment", "Post-treatment")) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black", size=1, alpha = 0.3)
```

Let's take a look at what this looks like considering dynamics events:
```{r, echo=FALSE}
Fig
```

Now we calculate the overall effects on innovative performance. The results are:
```{r, include=FALSE}
#Simple Aggregation Innovative performance
example_attgt <- att_gt(yname = "NoPatentsYearGUOtotal", tname = "CurrentYear", idname = "id", 
                        gname = "first.treat", xformla = ~1, data = DataLong_Subs_sim, alp=.01
)

agg.simple <- aggte(example_attgt, type = "simple", na.rm = TRUE)
```
```{r}
summary(agg.simple)
```

Let's see the effects considering dynamic events:
```{r, include=FALSE}
#1.1.2.Dynamic Effects and Event Studies
agg.es <- aggte(example_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) 
Fig<- ggdid(agg.es, title = "H2) All quartiles - Innovative performance") + 
  theme(legend.position="right") +
  ylab("Number of patents") + 
  xlab("Length of exposure") + 
  # ylim(-1, 4) +
  scale_color_manual(values=c("grey70","saddlebrown"),labels = c("Pre-treatment", "Post-treatment")) + 
  #labs(subtitle = "Effect on the number of patents")+
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r, echo=FALSE}
Fig
```

#### Moderating effects (non-standard)
Let's calculate moderating effects of relatedness on innovative performance. Starting with relatedness without any moderation (i.e., let's just look at what is the treatment effect of AI using a traditional did approach):
```{r, include=FALSE}
DataLong_Subs_sim$post_treatment <- ifelse(DataLong_Subs_sim$CurrentYear >= DataLong_Subs_sim$first.treat & 
                                               DataLong_Subs_sim$Group <= DataLong_Subs_sim$CurrentYear, 1, 0)

#Basic DiD model without the moderator for relatedness
model <- lm(Relatedness_Cos2 ~ treat * post_treatment, data = DataLong_Subs_sim)
```
```{r}
summary(model) 
```

Let's calculate now the treatment effect of AI using a traditional did approach for innovative performance:
```{r, include=FALSE}
model <- lm(NoPatentsYearGUOtotal ~ treat * post_treatment, data = DataLong_Subs_sim)
```
```{r}
summary(model) 
```

Finally, we estimate the moderating effects of relatedness on innovative performance. The effect of innovative performance is shown in the variable "treat:post_treatment", whereas the moderating effect of relatedness is shown in variable treat:post_treatment:Relatedness_Cos2.
```{r, include=FALSE}
model_moderation <- lm(NoPatentsYearGUOtotal ~ treat * post_treatment * Relatedness_Cos2, data = DataLong_Subs_sim)
```
```{r}
summary(model_moderation)
```

### 2.1.2.Standardized - Relatedness and number of patents regardless of sector
Let's now standardize the values and re estimate the effects for the same variables. Starting with relatedness:
```{r, include=FALSE}
DataLong_Subs_sim_standard <- DataLong_Subs_sim
DataLong_Subs_sim_standard[,c("Relatedness_Cos2", "NoPatentsYearGUOtotal")] <- 
  scale(DataLong_Subs_sim_standard[,c("Relatedness_Cos2", "NoPatentsYearGUOtotal")])

#Simple Aggregation Relatedness
example_attgt <- att_gt(yname = "Relatedness_Cos2", tname = "CurrentYear", idname = "id", gname = "first.treat",
                        xformla = ~1, data = DataLong_Subs_sim_standard, alp=.01)

agg.simple <- aggte(example_attgt, type = "simple", na.rm = TRUE)
```
```{r}
summary(agg.simple) 
```

Now, for innovative performance:
```{r, include=FALSE}
example_attgt <- att_gt(yname = "NoPatentsYearGUOtotal", tname = "CurrentYear", idname = "id", gname = "first.treat",
                        xformla = ~1,data = DataLong_Subs_sim_standard, alp=.01)
agg.simple <- aggte(example_attgt, type = "simple", na.rm = TRUE)
```
```{r}
summary(agg.simple)
```

#### Moderating effects (standardized)
Let's start with a traditional did approach to estimate the treatment effects of AI on relatedness:
```{r, include=FALSE}
DataLong_Subs_sim_standard$post_treatment <- ifelse(DataLong_Subs_sim_standard$CurrentYear >= DataLong_Subs_sim_standard$first.treat & 
                                             DataLong_Subs_sim_standard$Group <= DataLong_Subs_sim_standard$CurrentYear, 1, 0)

#Basic DiD model without the moderator for relatedness
model <- lm(Relatedness_Cos2 ~ treat * post_treatment, data = DataLong_Subs_sim_standard)
```
```{r}
summary(model)
```

Now innovative performance using a traditional did approach:
```{r, include=FALSE}
model <- lm(NoPatentsYearGUOtotal ~ treat * post_treatment, data = DataLong_Subs_sim_standard)
```
```{r}
summary(model)
```

Finally, we estimate the moderating effects of relatedness on innovative performance considering standardized values. The effect of innovative performance is shown in the variable "treat:post_treatment", whereas the moderating effect of relatedness is shown in variable treat:post_treatment:Relatedness_Cos2.
```{r, include=FALSE}
model_moderation <- lm(NoPatentsYearGUOtotal ~ treat * post_treatment * Relatedness_Cos2, data = DataLong_Subs_sim_standard)
```
```{r}
summary(model_moderation) 
```

## 2.2. Measuring effects across sectors 
```{r, include=FALSE}
rm(list=ls())
RCA_All_Years <-read.csv("Input_code/RCA_All_Years_Simplified.csv", sep = ";", header = TRUE, dec=",") 

mat_tech_rel <-read.csv2("Output_code/Data/Matrix_relatedness_technologies_to_AI.csv")#file we created before measuring the relatedness of AI to other technologies
mat_tech_rel <- mat_tech_rel[,c("X", "Artificial_Intelligence")] #select the AI and the other technologies columns
mat_tech_rel <- mat_tech_rel[mat_tech_rel$Artificial_Intelligence >0,] #from 646 to 515 with relatedness above 0
#let's pick the 5 codes with higher relatedness to AI:
AI_codes <- mat_tech_rel[mat_tech_rel$Artificial_Intelligence >.06,1] #5 codes

DataLong_Subs_sim <-read.csv("Input_code/Matched_companies.csv", sep = ";", header = TRUE, dec=",")
length(unique(DataLong_Subs_sim$id)) #2514 ids 

RCA_All_Years$AI_code <- ifelse(RCA_All_Years$Subclass %in% AI_codes, "AI_code", "Other_codes")

RCA_All_Years %<>% group_by(id,CurrentYear, AI_code) %>% 
  mutate(AIcodes = sum(RCA)) %>% 
  ungroup()

RCA_All_Years_treat_AI <- RCA_All_Years[RCA_All_Years$AI_code == "AI_code",]
RCA_All_Years_treat_AI <- distinct_at(RCA_All_Years_treat_AI, vars(id,CurrentYear), .keep_all = T)
RCA_All_Years_treat_AI <- RCA_All_Years_treat_AI[,c("id", "CurrentYear", "AIcodes")]

DataLong_Subs_sim <- left_join(DataLong_Subs_sim, RCA_All_Years_treat_AI, by = c("id", "CurrentYear"))

table(is.na(DataLong_Subs_sim$AIcodes)) #13607 F, 21589   T
#Replace NAs by 0:
DataLong_Subs_sim$AIcodes[is.na(DataLong_Subs_sim$AIcodes)] <- 0
table(is.na(DataLong_Subs_sim$AIcodes)) #35196 F

#Insert distance  measure
CategoriesNace <-read.csv("Output_code/Data/Distance_NACE_sectors_to_AI.csv", sep = ";", header = TRUE, dec=",")#[,c(-1)] #doesn't work, no significance
DataLong_Subs_sim$Nace_4d <- as.character(DataLong_Subs_sim$Nace_4d)
DataLong_Subs_sim <- left_join(DataLong_Subs_sim,CategoriesNace, by = "Nace_4d")

table(is.na(DataLong_Subs_sim$Quartile)) #33096        F  2100      T
table(DataLong_Subs_sim$Quartile) #bottom 9380              medium  11004            top 12712      

DataLong_Subs_sim$Quartile[is.na(DataLong_Subs_sim$Quartile)] <- "bottom"
table(is.na(DataLong_Subs_sim$Quartile)) #35196 F
table(DataLong_Subs_sim$Quartile) #bottom 11480             medium  11004            top 12712     

treat_test <-DataLong_Subs_sim[DataLong_Subs_sim$treat == 1,]
nontreat_test <-DataLong_Subs_sim[DataLong_Subs_sim$treat == 0,]
table(treat_test$Quartile) #bottom 5740    medium   5502    top 6356 
table(nontreat_test$Quartile) #bottom 5740    medium   5502    top 6356 
treat_test <- distinct_at(treat_test, vars(id,subclass), .keep_all = T)
nontreat_test <- distinct_at(nontreat_test, vars(id,subclass), .keep_all = T)
table(treat_test$Quartile) #bottom 410                    medium  393                      top 454     
rm(treat_test, nontreat_test)

DataLong_Subs_sim_group1 <- DataLong_Subs_sim[DataLong_Subs_sim$Quartile == "top" & is.na(DataLong_Subs_sim$Quartile) == F,]
DataLong_Subs_sim_group2 <- DataLong_Subs_sim[DataLong_Subs_sim$Quartile == "medium" & is.na(DataLong_Subs_sim$Quartile) == F,]
DataLong_Subs_sim_group3 <- DataLong_Subs_sim[DataLong_Subs_sim$Quartile == "bottom"& is.na(DataLong_Subs_sim$Quartile) == F,]

calculate_ci_and_significance <- function(att, se, group, variable_name) {
  # Confidence intervals at different significance levels
  ci_90_low <- att - 1.645 * se  # 90% confidence interval
  ci_90_high <- att + 1.645 * se
  
  ci_95_low <- att - 1.96 * se   # 95% confidence interval
  ci_95_high <- att + 1.96 * se
  
  ci_99_low <- att - 2.576 * se  # 99% confidence interval
  ci_99_high <- att + 2.576 * se
  
  # Determine the highest significance level
  significance <- ""
  
  if (ci_90_low > 0 | ci_90_high < 0) {
    significance <- "*"
  }
  if (ci_95_low > 0 | ci_95_high < 0) {
    significance <- "**"
  }
  if (ci_99_low > 0 | ci_99_high < 0) {
    significance <- "***"
  }
  if (!(ci_90_low > 0 | ci_90_high < 0)) {
    significance <- "" # No significance if not significant even at 90%
  }
  
  # Create a dataframe to store the results
  results_df <- data.frame(
    ATT = att,
    Std_Error = se,
    CI_90_Low = ci_90_low,
    CI_90_High = ci_90_high,
    CI_95_Low = ci_95_low,
    CI_95_High = ci_95_high,
    CI_99_Low = ci_99_low,
    CI_99_High = ci_99_high,
    Significance = significance,
    Group = group,
    Variable = variable_name
  )
  
  return(results_df)
}

#define the fixed variables
tname = "CurrentYear" 
idname = "id"
gname = "first.treat"

#define the possible groups
groups = c("DataLong_Subs_sim_group1","DataLong_Subs_sim_group2","DataLong_Subs_sim_group3")

#define the possible variables
variables = c("Relatedness_Cos2", #relatedness
              "NoPatentsYearGUOtotal", #innovative performance
              "Specializations_Usage", #usage of specializations
              "HigherUsage", #most used technology
              "Specializations_Number", #number of specializations
              "UniqueCodes", #for Sections
              "UniqueSubclass", #for 4-digit
              "Herfindahl",
              "Shannon",
              "AIcodes", #effect on the 5 codes most related to AI
              "No_AI_PatentsYearGUOtotal") #effect on number of AI patents

```

### 2.2.1.Calculate the effects Non-standardized

#### 2.2.1.1.Relatedness
Let's calculate the effects for relatedness first, considering the closest group.
Q1
```{r, include=FALSE}
####2.2.1.1.Relatedness----
#Group 1
variable_n = 1
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                        yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#summary(agg.simple)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#create the dataset:
results_df <- calculate_ci_and_significance(att, se, group, variable_name)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297

Fig<- ggdid(agg.es, title = "H3) Q1 - Relatedness") + 
  theme(legend.position="right") +
  ylab("Estimated effect on relatedness") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","steelblue3")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r}
summary(agg.simple)
Fig
results_df
```

IQR
```{r, include=FALSE}
#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297

Fig<-ggdid(agg.es, title = "H4) IQR - Relatedness") + 
  theme(legend.position="right") +
  ylab("Estimated effect on relatedness") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","green4")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r}
summary(agg.simple)
results_df
Fig
```

Q4
```{r, include=FALSE}
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297
Fig<- ggdid(agg.es, title = "H5) Q4 - Relatedness") + 
  theme(legend.position="right") +
  ylab("Estimated effect on relatedness") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","red4")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r}
summary(agg.simple)
results_df
Fig
```

#### 2.2.1.2.Innovative performance
Let's do the same for innovative performance, starting with the closest group.
Q1
```{r, include=FALSE}
#Group 1
variable_n = 2
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)
#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) 

Fig<- ggdid(agg.es, title = "H6) Q1 - Innovative performance") + 
  theme(legend.position="right") +
  ylab("Estimated effect on number of patents") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","steelblue3")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r}
summary(agg.simple)
results_df
Fig
```

IQR
```{r, include=FALSE}
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)
#Dynamic events
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297

Fig<-ggdid(agg.es, title = "H7) IQR - Innovative performance") + 
  theme(legend.position="right") +
  ylab("Estimated effect on number of patents") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","green4")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)
```
```{r}
summary(agg.simple)
results_df
Fig
```

Q4
```{r, include=FALSE}
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)
#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297

Fig<- ggdid(agg.es, title = "H8) Q4 - Innovative performance") + 
  theme(legend.position="right") +
  ylab("Estimated effect on number of patents") + 
  xlab("Length of exposure") + 
  scale_color_manual(values=c("grey70","red4")) + 
  labs(color   = "Treatment")+ 
  geom_vline(xintercept = 0, linetype="dotted", 
             color = "black", size=1, alpha = 0.3)

```
```{r}
summary(agg.simple)
results_df
Fig
```

Now we just measure all the effects of the remaining variables linked to dynamic capabilities, and put all of them together in a single table.
```{r, include=FALSE}
####2.2.1.3.Usage of specializations----
#Group 1
variable_n = 3
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.4.Most used technology----
#Group 1
variable_n = 4
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.5.Number of specializations----
#Group 1
variable_n = 5
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.6.Number of sections ----
#Group 1
variable_n = 6
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.7.Number of subclasses----
#Group 1
variable_n = 7
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.8.Herfindahl index----
#Group 1
variable_n = 8
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.9.Shannon index----
#Group 1
variable_n = 9
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.10.Number AI codes----
#Group 1
variable_n = 10
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.1.18. Number of AI patents----
#Group 1
variable_n = 11
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #
ggdid(agg.es) 

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #
ggdid(agg.es) 

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)
```
```{r}
results_df
```

These results are saved in the file named **"Results_Effects_non_stand.xlsx"**

### 2.2.2.Calculate the effects Standardized
Let's do the same for standardized effects, estimating all the effects at once and saving them into a table:
```{r, include=FALSE}
#standardize per group
DataLong_Subs_sim_group1[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                            "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")] <- 
  scale(DataLong_Subs_sim_group1[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                                    "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")])

DataLong_Subs_sim_group2[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                            "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")] <- 
  scale(DataLong_Subs_sim_group2[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                                    "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")])

DataLong_Subs_sim_group3[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                            "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")] <- 
  scale(DataLong_Subs_sim_group3[,c("Relatedness_Cos2", "Specializations_Usage", "HigherUsage","Specializations_Number",
                                    "Herfindahl", "Shannon", "NoPatentsYearGUOtotal", "UniqueCodes", "UniqueSubclass", "AIcodes", "No_AI_PatentsYearGUOtotal")])

####2.2.2.1.Relatedness----
#Group 1
variable_n = 1
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#create the dataset:
results_df <- calculate_ci_and_significance(att, se, group, variable_name)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #
ggdid(agg.es) 

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0719        0.0448    -0.0159      0.1598 
ggdid(agg.es) 

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)

agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.108        0.0431     0.0235      0.1925 *
ggdid(agg.es) 

####2.2.2.2.Innovative performance----
#Group 1
variable_n = 2
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.2826        0.1538    -0.0189      0.5841
ggdid(agg.es) 

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) 
ggdid(agg.es) 

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #0.0597        0.0357    -0.0103      0.1297
ggdid(agg.es) 

####2.2.2.3.Usage of specializations----
#Group 1
variable_n = 3
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.4.Most used technology----
#Group 1
variable_n = 4
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.5.Number of specializations----
#Group 1
variable_n = 5
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.6.Number of sections ----
#Group 1
variable_n = 6
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.7.Number of subclasses----
#Group 1
variable_n = 7
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.8.Herfindahl index----
#Group 1
variable_n = 8
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.9.Shannon index----
#Group 1
variable_n = 9
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.10.Number AI codes----
#Group 1
variable_n = 10
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

####2.2.2.11. Number of AI patents----
#Group 1
variable_n = 11
n_group = 1
group = print(groups[n_group], quote=FALSE)
variable_name <- variables[variable_n]
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group1 )
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #
ggdid(agg.es) 

#Group 2
n_group = 2
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group2)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)

#dynamic events:
agg.es <- aggte(estim_attgt, type = "dynamic", na.rm = TRUE)
summary(agg.es) #
ggdid(agg.es) 

#Group 3
n_group = 3
group = print(groups[n_group], quote=FALSE)
#estimate:
estim_attgt <- att_gt(tname = tname, idname = idname, gname = gname, 
                      yname = variables[variable_n], data = DataLong_Subs_sim_group3)
agg.simple <- aggte(estim_attgt, type = "simple", na.rm = TRUE)
#pick the estimate values:
att <- agg.simple$overall.att          # Average Treatment Effect on the Treated (ATT)
se <- agg.simple$overall.se            # Standard Error
#update dataset:
results_new <- calculate_ci_and_significance(att, se, group, variable_name)
results_df <- rbind(results_df, results_new)
```
```{r}
results_df
```

These results are saved in a file named **"Results_Effects_stand.xlsx"**

# 3.Descriptive statistics and correlations
Finally, let's recreate the descriptive statistics shown on the paper.
```{r, include=FALSE}
rm(list=ls())
FinalDataset <- read.csv("Input_code/Data_all_years_all_MNEs.csv", sep = ";", header = TRUE, dec=",")#[,c(-1)] #doesn't work, no significance
FinalDataset$Nace_4d <- as.character(FinalDataset$Nace_4d)
CategoriesNace <-read.csv("Output_code/Data/Distance_NACE_sectors_to_AI.csv", sep = ";", header = TRUE, dec=",")#[,c(-1)] #doesn't work, no significance

FinalDataset <- left_join(FinalDataset,CategoriesNace, by = "Nace_4d")
table(is.na(FinalDataset$Quartile)) #476620 F; 62820 T
table(FinalDataset$Quartile) #bottom 213880  medium  175220  top 87520     

FinalDataset$Quartile[is.na(FinalDataset$Quartile)] <- "bottom"
table(is.na(FinalDataset$Quartile)) #539440  
table(FinalDataset$Quartile) #bottom 276700     medium 175220       top 87520 
```

## 3.1.Statistics All data
Considering the whole dataset, we have:
```{r, include=FALSE}
FinalDataset_2019 <- FinalDataset[FinalDataset$CurrentYear== 2019,]
FinalDataset_summary <- FinalDataset_2019[,c("Relatedness_Cos2", "NoSubs_calculated", "NoSubsWithPatents", "Size_class", 
                                        "NoPatentsYearGUOtotal", "No_AI_PatentsYearGUOtotal","No_employees_Year",
                                        "Date_Incorporation", "Specializations_Usage", "HigherUsage", "Specializations_Number",
                                        "Herfindahl", "Shannon", "Quartile",
                                        "UniqueCodes", "UniqueSubclass")]
```
```{r}
st(FinalDataset_summary, group = "Size_class",  group.test = TRUE,
                 summ=c('mean(x)','median(x)','sd(x)','min(x)','pctile(x)[25]','pctile(x)[75]','max(x)'), out = 'return')

st(FinalDataset_summary, group = "Quartile",  group.test = TRUE,
               summ=c('mean(x)','median(x)','sd(x)','min(x)','pctile(x)[25]','pctile(x)[75]','max(x)'), out = 'return')
```

These last two tables are saved as **"Descriptive_statistics_all_MNEs_by_Size_class.csv"** and **"Descriptive_statistics_all_MNEs_by_Quartile.csv"**, respectively.

## 3.2.Statistics matched data
Considering only matched companies, we have:
```{r, include=FALSE}
rm(Size_class, Quartile, CategoriesNace)
DataLong_Subs_2006 <- read.csv("Input_code/Matched_companies.csv", sep = ";", header = TRUE, dec=",") #
#get the mean of the last 5 years
DataLong_Subs_2006 %<>% group_by(Company, subclass) %>% 
  mutate(across(NoPatentsYearGUOtotal,
                .fns = list(avg = ~ rollmean(.,k=5,fill=NA,align = 'center'))))

#new: Relatedness_lagged 
DataLong_Subs_2006 %<>% group_by(Company, subclass) %>% 
  mutate(NoPatentsYearGUOtotal_avg_fixed = lag(NoPatentsYearGUOtotal_avg)) %>% 
  mutate(Relatedness_lagged = lag(Relatedness_Cos2)) 

DataLong_Subs_2006 <- subset(DataLong_Subs_2006, select = -c(NoPatentsYearGUOtotal_avg) )
For_Match <- FinalDataset[,c("Company","CurrentYear","Quartile", "HigherUsage","Specializations_Usage", "Specializations_Number","Shannon","Herfindahl","NoSubs_calculated", "NoSubsWithPatents", "No_employees_Year",
                             "UniqueCodes", "UniqueSubclass")] #new 
DataLong_Subs_2006 <- left_join(DataLong_Subs_2006, For_Match, by=c("Company","CurrentYear"),na_matches="never")
rm(For_Match)

DataLong_Subs_2006 %<>% group_by(Company, subclass) %>% 
  mutate(N_specializations_lagged = lag(Specializations_Number.x)) 

DataLong_Subs_2006_summary <- DataLong_Subs_2006[,c("Relatedness_Cos2", "Size_class", "NoPatentsYearGUOtotal", "No_AI_PatentsYearGUOtotal",
                                                    "Company","treat","Date_Incorporation", "Group", "CurrentYear", 
                                                    "NoPatentsYearGUOtotal_avg_fixed", "Nace_4d", "YearFirstAdoption",
                                                    "HigherUsage.x","Specializations_Usage.x", "Specializations_Number.x","Shannon.x","Herfindahl.x","NoSubs_calculated", "NoSubsWithPatents",
                                                    "Quartile", "No_employees_Year",
                                                    "Relatedness_lagged", "N_specializations_lagged", 
                                                    "UniqueCodes.x", "UniqueSubclass.x" )] 

DataLong_Subs_2006_summary <- DataLong_Subs_2006_summary[DataLong_Subs_2006_summary$Group == DataLong_Subs_2006_summary$CurrentYear,]
DataLong_Subs_2006_summary <- subset(DataLong_Subs_2006_summary, select = -c(Company, Group,  YearFirstAdoption, Nace_4d) )#, "CurrentYear"
```
```{r}
st(DataLong_Subs_2006_summary,  group = "treat",  group.test = TRUE,
              summ=c('mean(x)','median(x)','sd(x)','min(x)','pctile(x)[25]','pctile(x)[75]','max(x)'), out = 'return')

st(DataLong_Subs_2006_summary,  group = "Quartile",  group.test = TRUE,
               summ=c('mean(x)','median(x)','sd(x)','min(x)','pctile(x)[25]','pctile(x)[75]','max(x)'), out = 'return')
st(DataLong_Subs_2006_summary,  group = "Size_class",  group.test = TRUE,
                 summ=c('mean(x)','median(x)','sd(x)','min(x)','pctile(x)[25]','pctile(x)[75]','max(x)'), out = 'return')
```

The last three tables are saved under the names **"Descriptive_statistics_matched_companies_Treated.csv"**, **"Descriptive_statistics_matched_companies_Quartile.csv"**, and **"Descriptive_statistics_matched_companies_Size_class.csv"**, respectively.

## 3.3.Analyse correlations
Finally, let's recreate the plots of correlations. Starting with the matched sample:
```{r, include=FALSE}
data_normalized <- DataLong_Subs_2006_summary[,c("Relatedness_Cos2", "HigherUsage.x", "Specializations_Usage.x", "Specializations_Number.x",
                                                 "Date_Incorporation","No_AI_PatentsYearGUOtotal", "NoPatentsYearGUOtotal")] 

names(data_normalized) <- c("Relatedness", "Usage of main code", "Usage of specializations",
                            "N. of specializations","Date of incorporation", "N. of AI patents","N. of patents") 
data_normalized <- scale(data_normalized)
corr_matrix <- cor(na.omit(data_normalized))
```
```{r, echo=FALSE}
ggcorrplot(corr_matrix, legend.title = "Correlation", hc.order=F,lab = TRUE)
```

And now for the whole dataset:

```{r, include=FALSE}
data_normalized <- FinalDataset_2019[,c("Relatedness_Cos2", "HigherUsage", "Specializations_Usage", "Specializations_Number",
                                   "Date_Incorporation","No_AI_PatentsYearGUOtotal", "NoPatentsYearGUOtotal")] 

names(data_normalized) <- c("Relatedness", "Usage of main code", "Usage of specializations",
                            "N. of specializations","Date of incorporation", "N. of AI patents","N. of patents") 
data_normalized <- scale(data_normalized)
corr_matrix <- cor(na.omit(data_normalized))
```
```{r, echo=FALSE}
ggcorrplot(corr_matrix, legend.title = "Correlation", hc.order=F,lab = TRUE)
```
